---
title: "Study1 YNQ (6 speakers)"
author: "Cong Zhang"
date: "`r Sys.Date()`"

output:
  html_document:
    toc: yes
    df_print: paged
    number_sections: yes
  pdf_document:
    toc: yes
editor_options:
  chunk_output_tune: inline
---

```{r libraries and paths, include = F}
knitr::opts_chunk$set(echo = FALSE)

library(reshape2)
library(ggpubr)
library(plotrix)    # std error function
library(plyr)       # revalue
library(dplyr)      # group_by and summarize function
library(lme4)       # linear mixed effect model
library(lmerTest)
library(kableExtra)
library(report)
library(effects)
source("C:/Users/sprin/Documents/R/scripts/load_data.R")
source("C:/Users/sprin/Documents/R/scripts/draw_curves.R")
source("C:/Users/sprin/Documents/R/scripts/pirate_plot.R")

```


```{r}
# set fig path and tone inventory
fig_path = "C:/Users/sprin/Dropbox (Personal)/Journal_Article/TJ_YNQ/Study_1/fig/"

#### load data
  m.data <- load_mean_data("C:/Users/sprin/Dropbox (Personal)/Journal_Article/TJ_YNQ/Study_1/data/mean_f0_m.txt")
  f.data <- load_mean_data("C:/Users/sprin/Dropbox (Personal)/Journal_Article/TJ_YNQ/Study_1/data/mean_f0_f.txt")
  data <- rbind(f.data, m.data)
  data$text[data$text=="aa"] <- "a"
  
  str(data)
  data$dur <- data$EndTime - data$StartTime
  
  data$tone_register <- ifelse(data$tone=="T1"|data$tone=="T3", "L", "H")
  data$tone_shape <- ifelse(data$tone=="T1"|data$tone=="T4", "HL", "LH")

  
```


```{r subset onset and rhyme data}
  data$syl_label <- as.factor(ifelse(data$text=="m", "O", "R"))
  ## divide data into onset and rhyme
  onset.data <- subset(data, syl_label == "O")
  rhyme.data <- subset(data, syl_label == "R")
```


```{r remove f0 range outliers}
# remove f0 range outliers

rhyme.HL <- rhyme.data %>% filter(tone=="T1"|tone=="T4")
rhyme.LH <- rhyme.data %>% filter(tone=="T2"|tone=="T3")

rhyme.HL$outlier <- ifelse((rhyme.HL$max.f0.time-rhyme.HL$min.f0.time < 0), "ok", "outlier")
rhyme.LH$outlier <- ifelse((rhyme.LH$max.f0.time-rhyme.LH$min.f0.time > 0), "ok", "outlier")

rhyme.data <- rbind(rhyme.HL, rhyme.LH)
rhyme.data$range.f0 <- ifelse(rhyme.data$outlier == "outlier", NA, rhyme.data$range.f0)
rhyme.data$range.f0.erb <- ifelse(rhyme.data$outlier == "outlier", NA, rhyme.data$range.f0.erb)

```


<a href="#top">Back to top</a>

# Descriptive data and summary tables

## Mean F0
```{r Mean F0}
## Mean F0: onset
onset_production_f0.mean <- onset.data %>% 
  dplyr::group_by(tune,tone) %>% 
  dplyr::summarize(f0.mean=mean(mean.f0.erb,na.rm=TRUE),
                   sd=sd(mean.f0.erb,na.rm=TRUE),
                   se=std.error(mean.f0.erb,na.rm=TRUE),
                   f0.max=max(mean.f0.erb,na.rm=TRUE), 
                   f0.min=min(mean.f0.erb,na.rm=TRUE))

onset_production_f0.mean

# kable(onset_production_f0.mean) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)%>%
#   save_kable(file = "./results/descriptive/onset_production_f0.mean.doc")


## Mean F0: rhyme
rhyme_production_f0.mean <- rhyme.data %>% 
  dplyr::filter(tune %in% c("S","Q")) %>% 
  dplyr::group_by(tune,tone) %>% 
  dplyr::summarize(f0.mean=mean(mean.f0.erb,na.rm=TRUE),
                   sd=sd(mean.f0.erb,na.rm=TRUE),
                   se=std.error(mean.f0.erb,na.rm=TRUE),
                   f0.max=max(mean.f0.erb,na.rm=TRUE), 
                   f0.min=min(mean.f0.erb,na.rm=TRUE))
rhyme_production_f0.mean
# kable(rhyme_production_f0.mean) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)%>%
#   save_kable(file = "./results/descriptive/rhyme_production_f0.mean.doc")

```

<a href="#top">Back to top</a>

## F0 range
```{r F0 range}
## F0 range: onset

onset_production_f0.range <- onset.data %>% 
  dplyr::filter(tune %in% c("S","Q")) %>% 
  dplyr::group_by(tune,tone) %>% 
  dplyr::summarize(f0.range=mean(range.f0.erb,na.rm=TRUE),
                   sd=sd(range.f0.erb,na.rm=TRUE),
                   se=std.error(range.f0.erb,na.rm=TRUE),
                   f0.max=max(range.f0.erb,na.rm=TRUE), 
                   f0.min=min(range.f0.erb,na.rm=TRUE))

onset_production_f0.range

# kable(onset_production_f0.range) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)%>%
#   save_kable(file = "./results/descriptive/onset_production_f0.range.doc")


## F0 Range: rhyme
rhyme_production_f0.range <- rhyme.data %>% 
  dplyr::filter(tune %in% c("S","Q")) %>% 
  dplyr::group_by(tune,tone) %>% 
  dplyr::summarize(f0.range=mean(range.f0.erb,na.rm=TRUE),
                   sd=sd(range.f0.erb,na.rm=TRUE),
                   se=std.error(range.f0.erb,na.rm=TRUE),
                   f0.max=max(range.f0.erb,na.rm=TRUE), 
                   f0.min=min(range.f0.erb,na.rm=TRUE))
rhyme_production_f0.range
# kable(rhyme_production_f0.range) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)%>%
#   save_kable(file = "./results/descriptive/rhyme_production_f0.range.doc")

```

<a href="#top">Back to top</a>

## Max F0
```{r Max F0}
## Max F0: onset
onset_production_f0.max <- onset.data %>% 
  dplyr::filter(tune %in% c("S","Q")) %>% 
  dplyr::group_by(tune,tone) %>% 
  dplyr::summarize(f0.max=mean(max.f0,na.rm=TRUE),
                   sd=sd(max.f0,na.rm=TRUE),
                   se=std.error(max.f0,na.rm=TRUE),
                   f0.max=max(max.f0,na.rm=TRUE), 
                   f0.min=min(max.f0,na.rm=TRUE))

onset_production_f0.max

# kable(onset_production_f0.max) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)%>%
#   save_kable(file = "./results/descriptive/onset_production_f0.max.doc")



## Max F0: rhyme
rhyme_production_f0.max <- rhyme.data %>% 
  dplyr::filter(tune %in% c("S","Q")) %>% 
  dplyr::group_by(tune,tone) %>% 
  dplyr::summarize(f0.max=mean(max.f0,na.rm=TRUE),
                   sd=sd(max.f0,na.rm=TRUE),
                   se=std.error(max.f0,na.rm=TRUE),
                   f0.max=max(max.f0,na.rm=TRUE), 
                   f0.min=min(max.f0,na.rm=TRUE))
rhyme_production_f0.max
# kable(rhyme_production_f0.max) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)%>%
#   save_kable(file = "./results/descriptive/rhyme_production_f0.max.doc")

```

<a href="#top">Back to top</a>

## Min F0
```{r Min F0}
## Min F0: onset
onset_production_f0.min <- onset.data %>% 
  dplyr::filter(tune %in% c("S","Q")) %>% 
  dplyr::group_by(tune,tone) %>% 
  dplyr::summarize(f0.min=mean(min.f0,na.rm=TRUE),
                   sd=sd(min.f0,na.rm=TRUE),
                   se=std.error(min.f0,na.rm=TRUE),
                   f0.max=max(min.f0,na.rm=TRUE), 
                   f0.min=min(min.f0,na.rm=TRUE))

onset_production_f0.min

# kable(onset_production_f0.min) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)%>%
#   save_kable(file = "./results/descriptive/onset_production_f0.min.doc")


## Min F0: rhyme
rhyme_production_f0.min <- rhyme.data %>% 
  dplyr::filter(tune %in% c("S","Q")) %>% 
  dplyr::group_by(tune,tone) %>% 
  dplyr::summarize(f0.min=mean(min.f0,na.rm=TRUE),
                   sd=sd(min.f0,na.rm=TRUE),
                   se=std.error(min.f0,na.rm=TRUE),
                   f0.max=max(min.f0,na.rm=TRUE), 
                   f0.min=min(min.f0,na.rm=TRUE))
rhyme_production_f0.min
# kable(rhyme_production_f0.min) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)%>%
#   save_kable(file = "./results/descriptive/rhyme_production_f0.min.doc")

```

<a href="#top">Back to top</a>

## Duration
```{r Duration}
## Duration: onset
onset_production_duration <- onset.data %>% 
  dplyr::filter(tune %in% c("S","Q")) %>% 
  dplyr::group_by(tune,tone) %>% 
  dplyr::summarize(length=mean(duration,na.rm=TRUE),
                   sd=sd(duration,na.rm=TRUE),
                   se=std.error(duration,na.rm=TRUE),
                   f0.max=max(duration,na.rm=TRUE), 
                   f0.min=min(duration,na.rm=TRUE))

onset_production_duration

# kable(onset_production_duration) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)%>%
#   save_kable(file = "./results/descriptive/onset_production_duration.doc")


## Duration: rhyme
rhyme_production_duration <- rhyme.data %>% 
  dplyr::filter(tune %in% c("S","Q")) %>% 
  dplyr::group_by(tune,tone) %>% 
  dplyr::summarize(length=mean(duration,na.rm=TRUE),
                   sd=sd(duration,na.rm=TRUE),
                   se=std.error(duration,na.rm=TRUE),
                   f0.max=max(duration,na.rm=TRUE), 
                   f0.min=min(duration,na.rm=TRUE))
rhyme_production_duration
# kable(rhyme_production_duration) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)%>%
#   save_kable(file = "./results/descriptive/rhyme_production_duration.doc")

```

# Pirate plots: mean values and distribution
```{r pirate plots, include= FALSE, echo=FALSE}
###########################################################
########################## plots ##########################
###########################################################
# change in source("C:/Users/sprin/Documents/R/scripts/pirate_plot.R") for colour settings
# use pdf_pirate in source("C:/Users/sprin/Documents/R/scripts/pirate_plot.R") to generate pdf

fig_path = "C:/Users/sprin/Dropbox (Personal)/Journal_Article/TJ_YNQ/Study_1/fig/pirate/"

onset.data$tune <- factor(onset.data$tune, levels = c("S", "Q"))
rhyme.data$tune <- factor(rhyme.data$tune, levels = c("S", "Q"))

#### meanf0: rhyme
output_file <- paste0(fig_path, "zi_Q_rhyme_meanF0.png")
input_data <- rhyme.data
dv <- rhyme.data$mean.f0.erb
Tune <- rhyme.data$tune
Tone<- rhyme.data$tone
title <- ''
x_lab <- "Tone × Tune"
y_lab <- "mean f0 (ERB)"
y_lim <- c(0,9)
lab_location<- 0.2
lab_size <- 1.2

pirate_png(output_file, input_data, dv, Tune, Tone, title, x_lab, y_lab, y_lim,lab_location, lab_size)

#### meanf0: onset
output_file <- paste0(fig_path, "zi_Q_onset_meanF0.png")
input_data <- onset.data
dv <- onset.data$mean.f0.erb
Tune <- onset.data$tune
Tone<- onset.data$tone
title <- ''
x_lab <- "Tone × Tune"
y_lab <- "mean f0 (ERB)"
y_lim <- c(0,9)
lab_location<- 0.2
lab_size <- 1.2

pirate_png(output_file, input_data, dv, Tune, Tone, title, x_lab, y_lab, y_lim,lab_location, lab_size)


#### f0Range: rhyme
output_file <- paste0(fig_path, "zi_Q_rhyme_f0range.png")
input_data <- rhyme.data
dv <- rhyme.data$range.f0.erb
Tune <- rhyme.data$tune
Tone<- rhyme.data$tone
title <- ''
x_lab <- "Tone × Tune"
y_lab <- "f0 range (ERB)"
y_lim <- c(0,9)
lab_location<- 0.2
lab_size <- 1.2

pirate_png(output_file, input_data, dv, Tune, Tone, title, x_lab, y_lab, y_lim,lab_location, lab_size)

#### f0Range: onset
output_file <- paste0(fig_path, "zi_Q_onset_f0range.png")
input_data <- onset.data
dv <- onset.data$range.f0.erb
Tune <- onset.data$tune
Tone<- onset.data$tone
title <- ''
x_lab <- "Tone × Tune"
y_lab <- "f0 range (ERB)"
y_lim <- c(0,9)
lab_location<- 0.2
lab_size <- 1.2

pirate_png(output_file, input_data, dv, Tune, Tone, title, x_lab, y_lab, y_lim,lab_location, lab_size)

#### duration: rhyme
output_file <- paste0(fig_path, "zi_Q_rhyme_duration.png")
input_data <- rhyme.data
dv <- rhyme.data$duration*1000
Tune <- rhyme.data$tune
Tone<- rhyme.data$tone
title <- ''
x_lab <- "Tone × Tune"
y_lab <- "duration (ms)"
y_lim <- c(0,550)
lab_location<- 10
lab_size <- 1.2

pirate_png(output_file, input_data, dv, Tune, Tone, title, x_lab, y_lab, y_lim,lab_location, lab_size)

#### duration: onset
output_file <- paste0(fig_path, "zi_Q_onset_duration.png")
input_data <- onset.data
dv <- onset.data$duration*1000
Tune <- onset.data$tune
Tone<- onset.data$tone
title <- ''
x_lab <- "Tone × Tune"
y_lab <- "duration (ms)"
y_lim <- c(0,550)
lab_location<- 10
lab_size <- 1.2

pirate_png(output_file, input_data, dv, Tune, Tone, title, x_lab, y_lab, y_lim,lab_location, lab_size)

#### maxf0: rhyme
output_file <- paste0(fig_path, "zi_Q_rhyme_maxF0.png")
input_data <- rhyme.data
dv <- rhyme.data$max.f0.erb
Tune <- rhyme.data$tune
Tone<- rhyme.data$tone
title <- ''
x_lab <- "Tone × Tune"
y_lab <- "max f0 (ERB)"
y_lim <- c(0,9)
lab_location<- 0.2
lab_size <- 1.2

pirate_png(output_file, input_data, dv, Tune, Tone, title, x_lab, y_lab, y_lim,lab_location, lab_size)


#### minf0: rhyme
output_file <- paste0(fig_path, "zi_Q_rhyme_minF0.png")
input_data <- rhyme.data
dv <- rhyme.data$min.f0.erb
Tune <- rhyme.data$tune
Tone<- rhyme.data$tone
title <- ''
x_lab <- "Tone × Tune"
y_lab <- "min f0 (ERB)"
y_lim <- c(0,9)
lab_location<- 0.2
lab_size <- 1.2

pirate_png(output_file, input_data, dv, Tune, Tone, title, x_lab, y_lab, y_lim,lab_location, lab_size)


```
# LMER

```{r subset data into onset and rhymes}
## divide data into onset and rhyme
onset.data <- subset(data, syl_label == "O")
rhyme.data <- subset(data, syl_label == "R")

```

<a href="#top">Back to top</a>

## MeanF0 


### ----- MeanF0: onset-----
```{r MeanF0:onset model, echo = T}
# for random effects
F0Mean.full <- lmer(mean.f0.erb ~ tone_register + tone_shape + tune + tune:tone_register + tune:tone_shape + (1+ tone_register:tune + tone_shape:tune + tune|speaker) +  (1 |utterance), onset.data, REML=FALSE)

F0Mean.mod1 <- lmer(mean.f0.erb ~ tone_register + tone_shape + tune + tune:tone_register + tune:tone_shape + (1+ tune|speaker) +  (1 |utterance), onset.data, REML=FALSE)

# final model
F0Mean.mod <- F0Mean.mod1

summary(F0Mean.mod)

anova(F0Mean.mod)

result_table <- as.data.frame(summary(F0Mean.mod)$coef)

for (i in 1:length(result_table[,5])){
  if (result_table[i,5] < 0.05 & result_table[i,5] > 0.01){
  result_table$sig[i] <- '*'
  } else if (result_table[i,5]<0.01 & result_table[i,5] > 0.001){
    result_table$sig[i] <- '**'
  } else if (result_table[i,5]<0.001){
    result_table$sig[i] <- '***'
  }
  else if (result_table[i,5] > 0.05){
    result_table$sig[i] <- ''
  }
  
  }



kable(result_table)%>% 
  kable_styling(bootstrap_options = "striped", full_width = F)



```

Report - summary:

```{r MeanF0:onset summary, echo = T}
F0Mean.mod%>% report()

```
significance of tone_shapeLH:tuneS tells you that difference between Q and S are different for LH tones and HL tones


Report - anova:

```{r MeanF0:onset anova, echo = T}
report(anova(F0Mean.mod))
plot(allEffects(F0Mean.mod), multiline=TRUE, ci.style="bars",
     lines=list(col=c("red", "blue"), alpha=0.5))
```


<a href="#top">Back to top</a>

### ----- MeanF0: rhyme-----
```{r MeanF0:rhyme model, echo = T}
# for random effects
F0Mean.full <- lmer(mean.f0.erb ~ tone_register + tone_shape + tune + tune:tone_register + tune:tone_shape + (1+ tone_register:tune + tone_shape:tune + tune|speaker) +  (1 |utterance), rhyme.data, REML=FALSE)

F0Mean.mod1 <- lmer(mean.f0.erb ~ tone_register + tone_shape + tune + tune:tone_register + tune:tone_shape + (1+ tune|speaker) +  (1 |utterance), rhyme.data, REML=FALSE)


# final model
F0Mean.mod <- F0Mean.mod1

summary(F0Mean.mod)

result_table <- as.data.frame(summary(F0Mean.mod)$coef)

for (i in 1:length(result_table[,5])){
  if (result_table[i,5] < 0.05 & result_table[i,5] > 0.01){
  result_table$sig[i] <- '*'
  } else if (result_table[i,5]<0.01 & result_table[i,5] > 0.001){
    result_table$sig[i] <- '**'
  } else if (result_table[i,5]<0.001){
    result_table$sig[i] <- '***'
  }
  else if (result_table[i,5] > 0.05){
    result_table$sig[i] <- ''
  }
  
  }



kable(result_table)%>% 
  kable_styling(bootstrap_options = "striped", full_width = F)



```

Report - summary:

```{r MeanF0:rhyme summary, echo = T}
F0Mean.mod%>% report()

```

Report - anova:

```{r MeanF0:rhyme anova, echo = T}
report(anova(F0Mean.mod))
plot(allEffects(F0Mean.mod), multiline=TRUE, ci.style="bars",
     lines=list(col=c("red", "blue"), alpha=0.5))
```

## F0range 

### ----- F0range: onset-----
```{r F0range:onset model, echo = T}
# for random effects
F0range.full <- lmer(range.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tone_register:tune + tone_shape:tune + tune|speaker) +  (1 |utterance), onset.data, REML=FALSE)

F0range.mod1 <- lmer(range.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tune|speaker) +  (1 |utterance), onset.data, REML=FALSE)
F0range.mod2 <- lmer(range.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1|speaker) +  (1 |utterance), onset.data, REML=FALSE)


# final model
F0range.mod <- F0range.mod2

summary(F0range.mod)

result_table <- as.data.frame(summary(F0range.mod)$coef)

for (i in 1:length(result_table[,5])){
  if (result_table[i,5] < 0.05 & result_table[i,5] > 0.01){
  result_table$sig[i] <- '*'
  } else if (result_table[i,5]<0.01 & result_table[i,5] > 0.001){
    result_table$sig[i] <- '**'
  } else if (result_table[i,5]<0.001){
    result_table$sig[i] <- '***'
  }
  else if (result_table[i,5] > 0.05){
    result_table$sig[i] <- ''
  }
  
  }



kable(result_table)%>% 
  kable_styling(bootstrap_options = "striped", full_width = F)



```

Report - summary:

```{r F0range:onset summary, echo = T}
F0range.mod%>% report()

```

Report - anova:

```{r F0range:onset anova, echo = T}
report(anova(F0range.mod))
plot(allEffects(F0range.mod), multiline=TRUE, ci.style="bars",
     lines=list(col=c("red", "blue"), alpha=0.5))
```
<a href="#top">Back to top</a>

### ----- F0range: rhyme-----
```{r F0range:rhyme model, echo = T}
# for random effects
F0range.full <- lmer(range.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tone_register:tune + tone_shape:tune + tune|speaker) +  (1 |utterance), rhyme.data, REML=FALSE)

F0range.mod1 <- lmer(range.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tune|speaker) +  (1 |utterance), rhyme.data, REML=FALSE)

# final model
F0range.mod <- F0range.mod1

summary(F0range.mod)

result_table <- as.data.frame(summary(F0range.mod)$coef)

for (i in 1:length(result_table[,5])){
  if (result_table[i,5] < 0.05 & result_table[i,5] > 0.01){
  result_table$sig[i] <- '*'
  } else if (result_table[i,5]<0.01 & result_table[i,5] > 0.001){
    result_table$sig[i] <- '**'
  } else if (result_table[i,5]<0.001){
    result_table$sig[i] <- '***'
  }
  else if (result_table[i,5] > 0.05){
    result_table$sig[i] <- ''
  }
  
  }



kable(result_table)%>% 
  kable_styling(bootstrap_options = "striped", full_width = F)



```

Report - summary:

```{r F0range:rhyme summary, echo = T}
F0range.mod%>% report()

```

Report - anova:

```{r F0range:rhyme anova, echo = T}
report(anova(F0range.mod))
plot(allEffects(F0range.mod), multiline=TRUE, ci.style="bars",
     lines=list(col=c("red", "blue"), alpha=0.5))
```

<a href="#top">Back to top</a>

## maxf0

### ----- maxf0: onset-----

```{r maxF0:onset model, echo = T}
# for random effects
Maxf0.full <- lmer(max.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tone_register:tune + tone_shape:tune + tune|speaker) +  (1 |utterance), onset.data, REML=FALSE)

Maxf0.mod1 <- lmer(max.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tune|speaker) +  (1 |utterance), onset.data, REML=FALSE)

Maxf0.mod2 <- lmer(max.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1|speaker) +  (1 |utterance), onset.data, REML=FALSE)

# final model
Maxf0.mod <- Maxf0.mod1

summary(Maxf0.mod)

result_table <- as.data.frame(summary(Maxf0.mod)$coef)

for (i in 1:length(result_table[,5])){
  if (result_table[i,5] < 0.05 & result_table[i,5] > 0.01){
  result_table$sig[i] <- '*'
  } else if (result_table[i,5]<0.01 & result_table[i,5] > 0.001){
    result_table$sig[i] <- '**'
  } else if (result_table[i,5]<0.001){
    result_table$sig[i] <- '***'
  }
  else if (result_table[i,5] > 0.05){
    result_table$sig[i] <- ''
  }
  
  }



kable(result_table)%>% 
  kable_styling(bootstrap_options = "striped", full_width = F)



```

Report - summary:

```{r maxF0:onset summary, echo = T}
Maxf0.mod%>% report()


```
significance of tone_shapeLH:tuneS tells you that difference between Q and S are different for LH tones and HL tones


Report - anova:

```{r maxF0:onset anova, echo = T}
report(anova(Maxf0.mod))
plot(allEffects(Maxf0.mod), multiline=TRUE, ci.style="bars",
     lines=list(col=c("red", "blue"), alpha=0.5))
```
<a href="#top">Back to top</a>

### ----- maxf0: rhyme-----

```{r maxF0:rhyme model, echo = T}
# for random effects
Maxf0.full <- lmer(max.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tone_register:tune + tone_shape:tune + tune|speaker) +  (1 |utterance), rhyme.data, REML=FALSE)

Maxf0.mod1 <- lmer(max.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tune|speaker) +  (1 |utterance), rhyme.data, REML=FALSE)

# final model
Maxf0.mod <- Maxf0.mod1

summary(Maxf0.mod)

result_table <- as.data.frame(summary(Maxf0.mod)$coef)

for (i in 1:length(result_table[,5])){
  if (result_table[i,5] < 0.05 & result_table[i,5] > 0.01){
  result_table$sig[i] <- '*'
  } else if (result_table[i,5]<0.01 & result_table[i,5] > 0.001){
    result_table$sig[i] <- '**'
  } else if (result_table[i,5]<0.001){
    result_table$sig[i] <- '***'
  }
  else if (result_table[i,5] > 0.05){
    result_table$sig[i] <- ''
  }
  
  }



kable(result_table)%>% 
  kable_styling(bootstrap_options = "striped", full_width = F)



```

Report - summary:

```{r maxF0:rhyme summary, echo = T}
Maxf0.mod%>% report()


```
significance of tone_shapeLH:tuneS tells you that difference between Q and S are different for LH tones and HL tones


Report - anova:

```{r maxF0:rhyme anova, echo = T}
report(anova(Maxf0.mod))
plot(allEffects(Maxf0.mod), multiline=TRUE, ci.style="bars",
     lines=list(col=c("red", "blue"), alpha=0.5))
```
<a href="#top">Back to top</a>

## minf0 


### ----- minf0: onset-----

```{r minF0:onset model, echo = T}
# for random effects
Minf0.full <- lmer(min.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tone_register:tune + tone_shape:tune + tune|speaker) +  (1 |utterance), onset.data, REML=FALSE)

Minf0.mod1 <- lmer(min.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tune|speaker) +  (1 |utterance), onset.data, REML=FALSE)
Minf0.mod2 <- lmer(min.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1|speaker) +  (1 |utterance), onset.data, REML=FALSE)

# final model
Minf0.mod <- Minf0.mod2

summary(Minf0.mod)

result_table <- as.data.frame(summary(Minf0.mod)$coef)

for (i in 1:length(result_table[,5])){
  if (result_table[i,5] < 0.05 & result_table[i,5] > 0.01){
  result_table$sig[i] <- '*'
  } else if (result_table[i,5]<0.01 & result_table[i,5] > 0.001){
    result_table$sig[i] <- '**'
  } else if (result_table[i,5]<0.001){
    result_table$sig[i] <- '***'
  }
  else if (result_table[i,5] > 0.05){
    result_table$sig[i] <- ''
  }
  
  }



kable(result_table)%>% 
  kable_styling(bootstrap_options = "striped", full_width = F)



```

Report - summary:

```{r minF0:onset summary, echo = T}
Minf0.mod%>% report()


```
significance of tone_shapeLH:tuneS tells you that difference between Q and S are different for LH tones and HL tones


Report - anova:

```{r minF0:onset anova, echo = T}
report(anova(Minf0.mod))
plot(allEffects(Minf0.mod), multiline=TRUE, ci.style="bars",
     lines=list(col=c("red", "blue"), alpha=0.5))
```
<a href="#top">Back to top</a>

### ----- minf0: rhyme-----

```{r minF0:rhyme model, echo = T}
# for random effects
Minf0.full <- lmer(min.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tone_register:tune + tone_shape:tune + tune|speaker) +  (1 |utterance), rhyme.data, REML=FALSE)

Minf0.mod1 <- lmer(min.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tune|speaker) +  (1 |utterance), rhyme.data, REML=FALSE)
Minf0.mod2 <- lmer(min.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1|speaker) +  (1 |utterance), rhyme.data, REML=FALSE)
Minf0.mod3 <- lmer(min.f0.erb ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1|speaker), rhyme.data, REML=FALSE)


# final model
Minf0.mod <- Minf0.mod3

summary(Minf0.mod)

result_table <- as.data.frame(summary(Minf0.mod)$coef)

for (i in 1:length(result_table[,5])){
  if (result_table[i,5] < 0.05 & result_table[i,5] > 0.01){
  result_table$sig[i] <- '*'
  } else if (result_table[i,5]<0.01 & result_table[i,5] > 0.001){
    result_table$sig[i] <- '**'
  } else if (result_table[i,5]<0.001){
    result_table$sig[i] <- '***'
  }
  else if (result_table[i,5] > 0.05){
    result_table$sig[i] <- ''
  }
  
  }



kable(result_table)%>% 
  kable_styling(bootstrap_options = "striped", full_width = F)



```

Report - summary:

```{r minF0:rhyme summary, echo = T}
Minf0.mod%>% report()


```
significance of tone_shapeLH:tuneS tells you that difference between Q and S are different for LH tones and HL tones


Report - anova:

```{r minF0:rhyme anova, echo = T}
report(anova(Minf0.mod))
plot(allEffects(Minf0.mod), multiline=TRUE, ci.style="bars",
     lines=list(col=c("red", "blue"), alpha=0.5))
```

<a href="#top">Back to top</a>

## duration

### ----- duration: onset-----
```{r Duration:onset model, echo = T}
# for random effects
Duration.full <- lmer(duration ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tone_register:tune + tone_shape:tune + tune|speaker) +  (1 |utterance), onset.data, REML=FALSE)

Duration.mod1 <- lmer(duration ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tune|speaker) +  (1 |utterance), onset.data, REML=FALSE)
Duration.mod2 <- lmer(duration ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1|speaker) +  (1 |utterance), onset.data, REML=FALSE)



# final model
Duration.mod <- Duration.mod2

summary(Duration.mod)

result_table <- as.data.frame(summary(Duration.mod)$coef)

for (i in 1:length(result_table[,5])){
  if (result_table[i,5] < 0.05 & result_table[i,5] > 0.01){
  result_table$sig[i] <- '*'
  } else if (result_table[i,5]<0.01 & result_table[i,5] > 0.001){
    result_table$sig[i] <- '**'
  } else if (result_table[i,5]<0.001){
    result_table$sig[i] <- '***'
  }
  else if (result_table[i,5] > 0.05){
    result_table$sig[i] <- ''
  }
  
  }



kable(result_table)%>% 
  kable_styling(bootstrap_options = "striped", full_width = F)



```

Report - summary:

```{r Dur:onset summary, echo = T}
Duration.mod%>% report()


```
significance of tone_shapeLH:tuneS tells you that difference between Q and S are different for LH tones and HL tones


Report - anova:

```{r Dur:onset anova, echo = T}
report(anova(Duration.mod))
plot(allEffects(Duration.mod), multiline=TRUE, ci.style="bars",
     lines=list(col=c("red", "blue"), lty=c("solid", "dotted"), alpha=0.5))
```
<a href="#top">Back to top</a>

### ----- duration: rhyme-----

```{r Duration:rhyme model, echo = T}
# for random effects
Duration.full <- lmer(duration ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tone_register:tune + tone_shape:tune + tune|speaker) +  (1 |utterance), rhyme.data, REML=FALSE)

Duration.mod1 <- lmer(duration ~ tone_register + tone_shape + tune + tone_register:tune + tone_shape:tune + (1+ tune|speaker) +  (1 |utterance), rhyme.data, REML=FALSE)

# final model
Duration.mod <- Duration.mod1

summary(Duration.mod)

result_table <- as.data.frame(summary(Duration.mod)$coef)

for (i in 1:length(result_table[,5])){
  if (result_table[i,5] < 0.05 & result_table[i,5] > 0.01){
  result_table$sig[i] <- '*'
  } else if (result_table[i,5]<0.01 & result_table[i,5] > 0.001){
    result_table$sig[i] <- '**'
  } else if (result_table[i,5]<0.001){
    result_table$sig[i] <- '***'
  }
  else if (result_table[i,5] > 0.05){
    result_table$sig[i] <- ''
  }
  
  }



kable(result_table)%>% 
  kable_styling(bootstrap_options = "striped", full_width = F)



```

Report - summary:

```{r Dur:rhyme summary, echo = T}
Duration.mod%>% report()


```
significance of tone_shapeLH:tuneS tells you that difference between Q and S are different for LH tones and HL tones


Report - anova:

```{r Dur:rhyme anova, echo = T}
report(anova(Duration.mod))
plot(allEffects(Duration.mod), multiline=TRUE, ci.style="bars",
     lines=list(col=c("red", "blue"), lty=c("solid", "dotted"), alpha=0.5))
```

